A 3D curvilinear skeletonization algorithm with application to path tracing

### 2012-11-29 application_to_path_tracing.tex
Premières corrections reviewer 2 et 3

$L$ is the radiance (a radiometric quantity that represents luminosity) from point $x$ toward direction $\Theta$ and $L_e$ is the emitted radiance (non null only on light sources). The point $r(x, \Phi)$ is the nearest visible point from $x$ in the direction $\Phi$ of the hemisphere $\Omega_x$. The $f_s$ function expresses how much luminosity is exchanged, on point $x$, between an incoming ray $\Phi$ and the outgoing ray $\Theta$. It represents the material properties of the surface at point $x$.

@@

The function $p$ is a probability density function (pdf) that is used to sample $\Phi$. This estimator is unbiased, meaning that the expected value $E[\langle L_r(x \rightarrow \Theta) \rangle]$ is equal to $L_r(x \rightarrow \Theta)$. The variance of the estimator expresses its quality and depends on the choosen pdf $p$. The best choice is a pdf that matches the shape of the function to integrate (ie. give high density to samples that have high values for the function and low density to samples that have low values).
The strategy of choosing an adapted pdf is called \myem{importance sampling}~\cite{Ka86} and is used in global illumination to improve the convergence speed of the algorithms.

@@

This computation is done multiple times for each pixel. We average the results and get an estimation of the mean radiance passing through the pixel and heading towards the camera.
A bad pdf would lead in picking directions that don't reach the light before the end of the recursion, and produce results with a lot of noise in the final image. In the next part, we explain how to produce a pdf based on the curvilinear skeleton.

@@

As stated in the introduction, a curvilinear skeleton of the void (with some preprocessing achieved on it) gives us information on which directions the light comes from. Given these directions, we can build a efficient pdf $p_{skel}$ and guide our rays by sampling the hemispheres with $p_{skel}$.

@@

%La, pas clair !!!
Let $L$ be a light source of the scene and $n_L$ the nearest node of the skeleton that is visible by $L$. For each node, we compute the shortest path to $n_L$ along the skeleton. To do so, we use the Dijkstra algorithm and weight the edges of the skeleton depending on a visibility criteria: the weight of an edge $e$ is $1$ if $e$ is visible from $n_L$ and $10$ else. It results that illuminated paths will be shorter than paths located in dark areas.

@@

>>>>

$L$ is the radiance (a radiometric quantity that represents luminosity) from point $x$ toward direction $\Theta$ and $L_e$ is the emitted radiance (non null only on light sources). The point $r(x, \Phi)$ is the nearest visible point from $x$ in the direction $\Phi$ of the hemisphere $\Omega_x$. The $f_s$ function expresses how much luminosity is exchanged, on point $x$, between an incoming ray $\Phi$ and the outgoing ray $\Theta$. It represents the material properties of the surface at $x$.

@@

The function $p$ is a probability density function (pdf) that is used to sample $\Phi$. This estimator is unbiased, meaning that the expected value $E[\langle L_r(x \rightarrow \Theta) \rangle]$ is equal to $L_r(x \rightarrow \Theta)$. The variance of the estimator expresses its quality and depends on the choosen pdf $p$. The best choice is a pdf that matches the shape of the function to integrate (ie. gives high density to samples that have high values for the function and low density to samples that have low values).
The strategy of choosing an adapted pdf is called \myem{importance sampling}~\cite{Ka86} and is used in global illumination to improve the convergence speed of the algorithms.

@@

This computation is done multiple times for each pixel. We average the results and get an estimation of the mean radiance passing through the pixel and heading towards the camera.
A bad pdf would lead in picking directions that do not reach the light before the end of the recursion, and produce results with a lot of noise in the final image. In the next part, we explain how to produce a pdf based on the curvilinear skeleton.

@@

As stated in the introduction, a curvilinear skeleton of the void (with some preprocessing performed on it) gives us information on which directions the light comes from. Given these directions, we can build a efficient pdf $p_{skel}$ and guide our rays by sampling the hemispheres with $p_{skel}$.

@@

%La, pas clair !!!
Let $L$ be the light source of the scene and $n_L$ the nearest node of the skeleton that is visible by $L$. For each node, we compute the shortest path to $n_L$ along the skeleton. To do so, we use the Dijkstra algorithm and weight the edges of the skeleton depending on a visibility criteria: the weight of an edge $e$ is $1$ if $e$ is visible from $n_L$ and $10$ else. It results that illuminated paths will be shorter than paths located in dark areas.

@@

The algorithm can be extended to multiple light sources by taking into account, for each node, only the closest light source when following the curvilinear skeleton path.

### 2012-11-29 skeleton_and_pathtracing.tex
Premières corrections reviewer 2 et 3

In the 3D voxel framework, objects are made of voxels. In the 3D cubical complex framework, objects are made of cubes, squares, lines and vertices. 
Let $\Z$ be the set of integers, we consider the family of sets $\mathbb{F}^1_0$ and $\mathbb{F}^1_1$, such that $\mathbb{F}^1_0 = \{\{a\} \suchthat a \in \Z\}$ and $\mathbb{F}^1_1 = \{ \{a, a+1\} \suchthat a \in \Z\}$. Any subset $f$ of $\Z^n$ such that $f$ is the cartesian product of $m$ elements of $\mathbb{F}^1_1$ and $(n-m)$ elements of $\mathbb{F}^1_0$ is called a face or an \myem{$m$-face} of $\Z^n$, $m$ is the dimension of $f$, we write $dim(f)=m$. A $0$-face is called a \myem{vertex}, a $1$-face is an \myem{edge}, a $2$-face is a \myem{square}, and a $3$-face is a \myem{cube}.

We denote by $\allfaces{n}$ the set composed of all faces in $\Z^n$. Given $m \in \dinterval{0}{n}$, we denote by $\subfaces{n}{m}$ the set composed of all $m$-faces in $\Z^n$.
Let $f \in \allfaces{n}$. We set $\cell{f} = \{g \in \allfaces{n}\vert g \subseteq f\}$, and $\cellstrict{f} = \cell{f} \setminus \{f\}$. Any element of $\cell{f}$ (resp. $\cellstrict{f}$) is \myem{a face of $f$} (resp. \myem{a proper face of $f$}.
The \myem{closure} of a set of faces $X$ is the set $\closure{X}=\union\{\cell{f} \vert f \in X\}$.

@@

Let $\complex{n}{Y}$, the complex $X$ \myem{collapses onto} $Y$ if there exists a sequence of complexes $(X_0,...,X_\ell)$ of $\allfaces{n}$ such that $X=X_0$, $Y=X_\ell$ and for all $i \in \dinterval{1}{\ell}, X_{i}$ is an elementary collapse of $X_{i-1}$. We also say, in this case, that $Y$ \myem{is a collapse of} $X$.
\end{definition}

@@

Given $S \subset \Zset^n$, the value of $\DD1{S}(x)$ of every $x \in S$ can be naively computed by performing successive morphological dilations of values of the map $\Dist1{S}$. A linear algorithm for computing the map $\DD1{S}$ (with regards to the size of the input image) was proposed in \cite{Chaussard_phd}, and will be explored further in details in a future paper.

@@

An exemple of these maps is shown on Fig.~\ref{fig::globalopening}.

@@

Informally, if $f$ is a 3-face, then $\cplDist1{Y}(f)$ is the length of the shortest 1-path between the voxel \quotes{corresponding} to $f$ and the set of voxels corresponding to $Y$.
The same way, we define $\cplDD1{Y}$ and $\cpldecent{Y}$.

>>>>

In the 3D voxel framework, objects are made of voxels. In the 3D cubical complex framework, objects are made of cubes, squares, lines and vertices. 
Let $\Z$ be the set of integers, we consider the family of sets $\mathbb{F}^1_0$ and $\mathbb{F}^1_1$, such that $\mathbb{F}^1_0 = \{\{a\} \suchthat a \in \Z\}$ and $\mathbb{F}^1_1 = \{ \{a, a+1\} \suchthat a \in \Z\}$. Any subset $f$ of $\Z^n$ such that $f$ is the Cartesian product of $m$ elements of $\mathbb{F}^1_1$ and $(n-m)$ elements of $\mathbb{F}^1_0$ is called a face or an \myem{$m$-face} of $\Z^n$, $m$ is the dimension of $f$, we write $dim(f)=m$. A $0$-face is called a \myem{vertex}, a $1$-face is an \myem{edge}, a $2$-face is a \myem{square}, and a $3$-face is a \myem{cube}.

We denote by $\allfaces{n}$ the set composed of all faces in $\Z^n$. Given $m \in \dinterval{0}{n}$, we denote by $\subfaces{n}{m}$ the set composed of all $m$-faces in $\Z^n$.
Let $f \in \allfaces{n}$. We set $\cell{f} = \{g \in \allfaces{n}\vert g \subseteq f\}$, and $\cellstrict{f} = \cell{f} \setminus \{f\}$. Any element of $\cell{f}$ (resp. $\cellstrict{f}$) is \myem{a face of $f$} (resp. \myem{a proper face of $f$}).
The \myem{closure} of a set of faces $X$ is the set $\closure{X}=\union\{\cell{f} \vert f \in X\}$.

@@

Let $\complex{n}{Y}$. The complex $X$ \myem{collapses onto} $Y$ if there exists a sequence of complexes $(X_0,...,X_\ell)$ of $\allfaces{n}$ such that $X=X_0$, $Y=X_\ell$ and for all $i \in \dinterval{1}{\ell}, X_{i}$ is an elementary collapse of $X_{i-1}$. We also say, in this case, that $Y$ \myem{is a collapse of} $X$.
\end{definition}

@@

Given $S \subset \Zset^n$, the value of $\DD1{S}(x)$ of every $x \in S$ can be naively computed by performing successive morphological dilations of values of the map $\Dist1{S}$. A linear algorithm for computing the map $\DD1{S}$ (with regard to the size of the input image) was proposed in \cite{Chaussard_phd}, and will be explored further in details in a future paper.

@@

An example of these maps is shown on Fig.~\ref{fig::globalopening}.

@@

Informally, if $f$ is a 3-face, then $\cplDist1{Y}(f)$ is the length of the shortest 1-path between the voxel \quotes{corresponding} to $f$ and the set of voxels corresponding to $Y$.
In the same way, we define $\cplDD1{Y}$ and $\cpldecent{Y}$.
